skater: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2021-07-19 paper/paper.Rmd
refer to suppl materials in ped2kinpair and plot_pedigree h/t @ahhgust

The skater package has several functions for importing, parsing, and analyzing pedigree data. Pedigrees define familial relationships in a hierarchical structure. Many genomics tools for working with pedigrees start with a .fam file, which is a tabular format with one row per individual and columns for unique IDs of the mother, father, and the family unit. The skater package contains the function `read_fam()` to read in a PLINK-formatted .fam file and another function `fam2ped()` to convert the content into a pedigree object as a nested tibble with one row per family. All pedigree processing from skater internally leverages a data structure from the kinship2 package [@kinship2]. Further functions such as `plot_pedigree()` produce a multi-page PDF drawing a diagram of the pedigree for each family, while `ped2kinpair()` produces a pairwise list of relationships between all individuals in the data with the expected kinship coefficients for each pair.

>>>>

The skater package has several functions for importing, parsing, and analyzing pedigree data. Pedigrees define familial relationships in a hierarchical structure. Many genomics tools for working with pedigrees start with a .fam file, which is a tabular format with one row per individual and columns for unique IDs of the mother, father, and the family unit. The skater package contains the function `read_fam()` to read in a PLINK-formatted .fam file and another function `fam2ped()` to convert the content into a pedigree object as a nested tibble with one row per family. All pedigree processing from skater internally leverages a data structure from the kinship2 package [@kinship2]. Further functions such as `plot_pedigree()` produce a multi-page PDF drawing a diagram of the pedigree for each family, while `ped2kinpair()` produces a pairwise list of relationships between all individuals in the data with the expected kinship coefficients for each pair (see Supplementary Material).
